ms2

### 2017-05-03 ms2/ms2.Rmd
modernizing ms2
- Use states mainly (HRRs are more noisy)
- Use a short-list of bug/drug candidates
- Collect data from all years

```{r load_abg}
resistance_groups = read_tsv('../states/resistance/resistance_groups.tsv')

@@

possible_bug_drug = read_tsv('bug_drug.tsv')

# Keep only bug/drug combinations that are in at least 75 HRRs
good_combos = possible_bug_drug %>%
  left_join(abg, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, hrr) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= 75)

@@

I similarly joined the consumption drugs into similar classes. I'm looking at these `r nrow(good_combos)` bug/drug combinations:

@@

# swo> why do I need to redo this filtering?
results = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  group_by(bug, drug_group) %>%
  do(models(.)) %>%
  ungroup

@@

```{r spearman_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj, n_data) %>%
  kable
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj, n_data) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.adj) %>%
  kable
```

@@

```{r multivariate_models, cache=FALSE, eval=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

>>>>

```{r load_abg}
resistance_groups = read_tsv('resistance_groups.tsv')

@@

possible_bug_drug = read_tsv('bug_drug2.tsv')

# Keep only bug/drug combinations that are in at least 75 HRRs
min_n_states = 35
good_combos = possible_bug_drug %>%
  left_join(abg, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)

@@

I similarly joined the consumption drugs into similar classes.

I started by considering these bug/drug combinations:

`r kable(possible_bug_drug)`

Then I filtered to keep only those bug/drug combinations that were present in `r min_n_states` states. That means I'm looking at these `r nrow(good_combos)` bug/drug combinations:

@@

results = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  group_by(bug, drug_group) %>%
  do(models(.)) %>%
  ungroup

@@

```{r spearman_models, cache=FALSE}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n_data) %>%
  kable
```

```{r}
results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  ggplot(aes(x=estimate, y=-log10(p.adj))) + geom_point() +
  geom_hline(yintercept=-log10(0.05), col='red')
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n_data) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.adj < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

```{r}
results %>%
  filter(model=='univariate') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  ggplot(aes(x=estimate, y=-log10(p.adj))) + geom_point() +
  geom_hline(yintercept=-log10(0.05), col='red')
```

@@

```{r multivariate_models, cache=FALSE}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.adj) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```
